\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\title{On The Nature of the World}
\label{first}
\author{Jack Hu}
\usepackage{ctex}
\begin{document}
	\maketitle
	\author
	\section{The Origin of Our World}
It's been a long topic since I have learned of the machenism of our world.Scientists in our area have always wanted to explore the machanism of the universe.For instice,How did our world come into being? \CTeX
	\subsection{What is our world made of?}
	\subsection{}
	only a few elements can be permanent magnets,iron is one.Copper is not.But if you Pass an eletric current through any metal,it becomes a magnet,an eletromagnet.
	But How does this work?well strangely enough,it's a consequence of special relativity.
	\paragraph{Special Relativity}
	\subparagraph{}
	Special relativity is the fact that in our universe,length and time aren't absolute.They are perceived differently by observers moving relative to each other,hence,telativity.
	for example,if you measure carefully enough.You'll find that time passes slower for observers moving relative to you.
	\subparagraph{}Hey Jack,when did you last shave?
	Six hours ago.Actually it was five hours,59.9999999999999999 seconds.
	And moving objects are also contracted in their direction of motion."You are looking slim!""Only in your frame of reference."SO when an object is moving relative to you,it actually takes up less space than when it's not moving.And even though this effect is obviously way tinier than we have shown.
	Length contraction is what makes an electromagnet work.
\end{document}